manuscript_modelling_and_plots_takeovers

### 2024-08-28 manuscript_and_modelling_plots_takeovers.Rmd
resizing figures for manuscript

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig5.tiff"), plot = fig5, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
```

@@

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig6.tiff"), plot = fig6, width = 16, height = 11, units = 'cm', dpi = 300, type = 'cairo')
```

>>>>

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig5.tiff"), plot = fig5, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
```

@@

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig6.tiff"), plot = fig6, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
```
